Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-17 MScDiplom_Lemenkova.tex
added work flowchart diagram for stat analysis

\vspace{5em}

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
	\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
	\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
	\item WASI Water Color Simulator, for modelling optical water properties under changing environment
	\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
	\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
	\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
	\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
	\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
	\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
	\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
	\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
	\item \href{http://gretl.sourceforge.net/}{Gretl: Gnu Regression, Econometrics and Time-series Library} for statistic analysis
\end{itemize}
\pagebreak

@@

\subsubsection{Statistical analysis of the observational data and hypothesis testing}
The total amount of measured data was large and included following datasets made using
hyperspectral radiometer Ramses: 350 measuremetn sets of P.oceanica reflectance for 14th Oct (Tab.\ref{tab:32}), 400
sets of P.oceanica reflectance for 15th Oct (Tab.\ref{tab:33}), 84 datasets for seawater reflectance with sediments, 105
datasets for seawater reflectance without sediments, 87 sets for spectral reflectance of carbonat sand.
A statistical approach is evidently necessary for the proper processing of such amounts of data. 
Statistical pre-processing of large sets of serial data enables to generalyse data by using the most typical and predicted values of
spectral reflectance for further calculations, and to get rid of the extreme values, noise and errors.
The statistical calculators were mainly made by means of Gretle and SPSS. 
The Open Office was used for preliminary data view and preprocessing, and included following computations
at each data set (for example, Tab.\ref{tab:31}) with summary outcome of mean, median, Q1 and Q3, standard deviation, min and max values (Tab.\ref{tab:4}). \\
The statistical pre-processing and analysis were made to display the mean values of spectral reflectances,
which were used for comparison with reflectance data of various seafloor cover types as well as
seawater with and without sediment (e.g. Tab.\ref{tab:2}).
In the statistical anlysis of the raw observed data pool of the values of spectral reflectances (about 400 single measurements for P.oceanica, e.g. Tab.\ref{tab:10}), we summarize their complexity by concentrating on some simple numerical characteristics that they possess, i.e. parameters. Examples are the mean and variance of a probability distribution of measurements dataset (for example, Tab.\ref{tab:16}). We divided the total data pool into datasets of 25 measurements for more convenience and ease of use, both for P.oceanica and carbonate sand. The mean of a probability distribution of spectral reflectance describes the average value of the random variable over all of its possible realizations (Appendices).  Conceptually, there are an infinite number of such realizations, therefore parameters are not known to us. However, in the statistical analysis of the observed data our goal is to estimate these parameters using a finite amount of information available to us: fieldwork observations. \\

>>>>

\vspace{4em}

\textbf{Software and utilities used in the current work}:\\
\begin{itemize}
	\item \href{http://www.esri.com/software/arcgis/index.html}{ArcGIS 10.0}: mapping, data integration and spatial analysis
	\item \href{http://www.erdas.com/products/ERDASIMAGINE/ERDASIMAGINE/Details.aspx}{Erdas Imagine}: imagery processing and classification
	\item WASI Water Color Simulator, for modelling optical water properties under changing environment
	\item \href{http://welcome.hp.com/country/us/en/prodserv/handheld.html}{iPAQ} and GPS for data capture during the fieldwork
	\item \href{http://www.bibtex.org/de/}{BibTeX}, for management of bibliography and reference database
	\item \href{http://www.latex-project.org/}{\LaTeX}, for document typesetting, formatting and performing pdf output
	\item \href{http://www.python.org/}{Python language}, for writing auxiliary scripts (e.g. raw data interpolation)
	\item \href{http://www.gnuplot.info/}{Gnuplot} for plotting graphs
	\item \href{http://www.openoffice.org/}{Open Office} : document typesetting, data preprocessing and preliminary statistical evalution
	\item \href{http://calc2latex.sourceforge.net/}{Calc2LaTeX} : converting spreadsheets into \LaTeX environment
	\item \href{http://www.spss.com/}{SPSS (PASW Statistics 18)} : statistical data edition and analysis 
	\item \href{http://gretl.sourceforge.net/}{Gretl: Gnu Regression, Econometrics and Time-series Library} for statistic analysis
	\item \href{http://staruml.sourceforge.net/en/}{StarUML}: modelling flowchart diagrams for work algorithms
\end{itemize}
\pagebreak

@@

\subsubsection{Statistical analysis of the observational data and hypothesis testing}
The total amount of measured data was large and included following datasets made using
hyperspectral radiometer Ramses: 350 measuremetn sets of P.oceanica reflectance for 14th Oct (Tab.\ref{tab:32}), 400
sets of P.oceanica reflectance for 15th Oct (Tab.\ref{tab:33}), 84 datasets for seawater reflectance with sediments, 105
datasets for seawater reflectance without sediments, 87 sets for spectral reflectance of carbonat sand.
A statistical approach is evidently necessary for the proper processing of such amounts of data. 
Statistical pre-processing of large sets of serial data enables to generalyse data by using the most typical and predicted values of
spectral reflectance for further calculations, and to get rid of the extreme values, noise and errors.
The statistical calculators were mainly made by means of Gretle and SPSS. 
The Open Office was used for preliminary data view and preprocessing, and included following computations
at each data set (for example, Tab.\ref{tab:31}) with summary outcome of mean, median, Q1 and Q3, standard deviation, min and max values (Tab.\ref{tab:4}). \\
The statistical pre-processing and analysis were made to display the mean values of spectral reflectances,
which were used for comparison with reflectance data of various seafloor cover types as well as
seawater with and without sediment (e.g. Tab.\ref{tab:2}).
In the statistical anlysis of the raw observed data pool of the values of spectral reflectances (about 400 single measurements for P.oceanica, e.g. Tab.\ref{tab:10}), we summarize their complexity by concentrating on some simple numerical characteristics that they possess, i.e. parameters. Examples are the mean and variance of a probability distribution of measurements dataset (for example, Tab.\ref{tab:16}). We divided the total data pool into datasets of 25 measurements for more convenience and ease of use, both for P.oceanica and carbonate sand. The mean of a probability distribution of spectral reflectance describes the average value of the random variable over all of its possible realizations (Appendices).  Conceptually, there are an infinite number of such realizations, therefore parameters are not known to us. However, in the statistical analysis of the observed data our goal is to estimate these parameters using a finite amount of information available to us: fieldwork observations. \\

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45, angle=90]{UML_StatAn.jpg}
	\caption{Work Flowchart Diagram illustrating algorithm of the Statistical Analysis applied towards the observation dataset (\href{http://staruml.sourceforge.net/en/}{StarUML})}
	\label{fig:34}
\end{figure}
